Market-based Mechanisms for Resource Scheduling

### 2013-12-18 paper/paper.tex
Spellecheck, more changes.

\maketitle
\begin{abstract}
Existing cluster managers typically allocate resources
based on a fairness criterion such as dominant resource fairness. 
However, this approach makes it difficult to accomodate complex requirements
without substantially increasing the complexity of the scheduler itself.
Standard approaches to this challenge compromise the efficiency
and fairness guarantees that make these simple scheduling policies attractive.

@@

Large-scale computing clusters offer the potential for greater efficiency through
pooling of computational resources, but must contend with the problem of
allocating these resources to users with competitive and potentially
incompatible demands. Such conflicts are typically arbitrated by some \emph{fairness}
criterions, such as dominant resource fairness (DRF) \cite{drf}, which benefit from their
simplicity, efficiency, and non-manipulability. Unfortunately, when applied in
realistic settings --- when dealing with inhomogeneous resources, time-varying
demands or deadlines, requirements for data locality, etc.---typical implementations
of these systems cease to be either
efficient or non-manipulable.

@@

\subsection{Motivating examples}

@@

There have bene many ad hoc proposals to address some of these difficulties.
For example, Jockey is a system which accomodates deadlines in a fair-share
scheduler by increasing the allotted shares for users which are appraoching
a deadline.
However, these techniques tend to violate the theoretical guarantees
of the underlying systems more starkly, and to require extensive tuning
in order to achieve good performance.
We seek a more general framework for addressing these difficulties.

Similarly, we might cope with the need for pre-emption by using various
heuristics to minimize the extent of overhead associated with evicting a running
task.
These heuristics may work well in practice, but are also likely to require
tuning and to be sensitive to the exact nature of the cluster.

@@

A naive representation of this function would use an exponential amount of
space. While we can consider several methods greatly varying in
complexity for encoding this function more compactly, we use the following
two-level representation:
\begin{itemize}
  \item A list of \emph{tasks}, with the assumption that a framework's
    willingness to pay for any set of tasks is simply the total
    willingness to pay for tasks in that set.
  \item For each task a list of possible resources which can be used to perform
    that task, together with a willingness to pay for that set of resources.
\end{itemize}
While this obviously cannot represent all possible $\mathcal{B}$, it still
allows enough flexibility to cover all of the applications we allude to
in the paper---to handle dealdines, inhomogeneous resources, fragmentation,
tasks of differing priorities, and so on.

@@

\paragraph{Adjusting bids} To modify the 
default policy to accomodate inhomogeneous resources,
times, or tasks, we can simply modify framework's
bids to adjust for the desirability of the resource being
purchased or the importance of the purpose they are being used for.

@@

\paragraph{Defensive bidding} One negative consequence of using a closed economy,
in which the frameworks bid using currency which is entirely internal to the cluster,
%XXX mention this distinction elsewhere, and the fact that we can do either
is the possibility of \emph{hoarding}, in which one framework
declines to use any resources during a certain period so that it can amass
a much larger budget than any other resources.
It can then spend this budget at a future point in order to monopolize the cluster,
which may have undesirable conseuqences for frameworks that need uninterrupted service.

This can be prevented by using an appropriate bidding strategy
(in general we recommend modifying bidding strategies to achieve a desired
function whenever possible and leaving the scheduler itself as simple as possible).
A defensive bidder $A$ who receives an income equal to a $p$ fraction
of the cluster's resources can ensure the following invariant:
during any window of length $T$, $A$ spends roughly $p$ times the total amount
spent by all frameworks, and at every point in time $A$'s reserves are roughly equal to $p$
times the total reserves of all frameworks (where $T$ is an upper bound on how frequently auctions are conducted,
either the maximum length of a task or the period of time after which the resources used by a task
will be reauctioned and potentially revoked).
In fact the second invariant follows from the first, which can be approximately attained
by simply scaling all bids during an interval of time $T$ to the appropriate level.

@@

By the definition of our auction, the price $p_B$ exceeds user A's willingness to pay for resources $R_B$ 
(or else user A's proxy would have continued bidding and the auction would not have concluded), 
while the price $p_A$ is less than user A's willingness to pay for resources $R_A$ 
(or else user A's proxy would have stopped bidding earlier). 
In particular, user A prefers their package to user B's package. 
Since at the start of the round user A preferred their allocation at their price to user B's allocation at user B's price, 
this property also holds at the end of the round. 
In this step we rely on our assumption that user A's valuations for their own holdings do not change after the auction is announced 
(otherwise it may be possible for user A to become envious in between rounds as more information is revealed, rather than during a round of the auction). 
We note in passing that similar assumptions are required to prove that DRF is envy-free in the dynamic setting,
even in a simple rather than realistic enviornment.
\qed
\end{pproof}

@@

When pricing information is provided, we show that the market-based mechanism can provide better performance than in DRF. As discussed in Section TODO, there are many situations in which prices can be used to better encapsulate a framework's preferences. As a case study, we investigate one particular scenario of inhomogeneous performing resources.

@@

\subsection{Grid computing}
Job schedulers like TORQUE \cite{torque}, Condor \cite{condor}, and LSF
\cite{lsf} have long been used for solving the problem of resource allocation
within a high-performance-computing (HPC) or grid-computing environment.
For the most part, they do not use a two-level scheduling model like we do but
instead operate as a queue for predefined jobs which are run as resources become
available. Machines and job requirements also tend to show more homogeniety
within such environments (for example, the ratio between CPU, memory, and disk),
so sthe amount of optimization possible with pricing is lower.

@@

More generally, fair division is the problem in economics of dividing a set of
resources equitably among a set of people. Our problem differs somewhat from
fair division in that we don't seek to allocate every bit of the cluster to the
set of users. We assume that a user might be happy to have received nothing if
their value of gaining resources was too low compared to the others, since the
user keeps some amont of money unspent as a a result.

One of the economic fair division solutions is CEEI~\cite{moulin2004fair}, or
competitive equilibrium from equal incomes. This mechanism emulates a market
where participants initially receive an equal amount of resources and trade some
of them until each has the desired amount of resources. CEEI's use of a market
differs significantly from ours in that we do not use it only as a vehicle for
achieving a fair allocation, but also for frameworks to express their
preferences in a fine-grianed way using prices and willingness to pay.

@@

In our evaluation, we showed through simulation the benefits of our protocol in the specific case of inhomogenous performing resources. However, there are a number of other user constraints that should theoretically be better expressed using prices than existing methods. Future work would be to experimentally evaluate such cases. A few such user constraints include deadlines and varying latency sensitivities, differential service guarantees, deadweight losses of evictions, costs of fragmenting jobs, various execution types (e.g. speculative vs essential execution), and co-location of data or other important resources.

@@

\section{Acknowledgement}

>>>>

\maketitle
\begin{abstract}
Existing cluster managers typically allocate resources
based on a fairness criterion such as dominant resource fairness. 
However, this approach makes it difficult to accommodate complex requirements
without substantially increasing the complexity of the scheduler itself.
Standard approaches to this challenge compromise the efficiency
and fairness guarantees that make these simple scheduling policies attractive.

@@

Large-scale computing clusters offer the potential for greater efficiency through
pooling of computational resources, but must contend with the problem of
allocating these resources to users with competitive and potentially
incompatible demands. Such conflicts are typically arbitrated by some \emph{fairness}
criteria, such as dominant resource fairness (DRF) \cite{drf}, which benefit from their
simplicity, efficiency, and non-manipulability. Unfortunately, when applied in
realistic settings --- when dealing with inhomogeneous resources, time-varying
demands or deadlines, requirements for data locality, etc.---typical implementations
of these systems cease to be either
efficient or non-manipulable.

@@

\subsection{Motivating examples}\label{examples}

@@

There have been many ad hoc proposals to address some of these difficulties.
For example, Jockey is a system which accommodates deadlines in a fair-share
scheduler by increasing the allotted shares for users which are approaching
a deadline.
However, these techniques tend to violate the theoretical guarantees
of the underlying systems more starkly, and to require extensive tuning
in order to achieve good performance.
We seek a more general framework for addressing these difficulties.

Similarly, we might cope with the need for preemption-  by using various
heuristics to minimize the extent of overhead associated with evicting a running
task.
These heuristics may work well in practice, but are also likely to require
tuning and to be sensitive to the exact nature of the cluster.

@@

A naive representation of this function would use an exponential amount of
space. While we can consider several methods greatly varying in
complexity for encoding this function more compactly, we use the following
two-level representation:
\begin{itemize}
  \item A list of \emph{tasks}, with the assumption that a framework's
    willingness to pay for any set of tasks is simply the total
    willingness to pay for tasks in that set.
  \item For each task a list of possible resources which can be used to perform
    that task, together with a willingness to pay for that set of resources.
\end{itemize}
While this obviously cannot represent all possible $\mathcal{B}$, it still
allows enough flexibility to cover all of the applications we allude to
in the paper---to handle deadlines, inhomogeneous resources, fragmentation,
tasks of differing priorities, and so on.

@@

\paragraph{Adjusting bids} To modify the 
default policy to accommodate inhomogeneous resources,
times, or tasks, we can simply modify framework's
bids to adjust for the desirability of the resource being
purchased or the importance of the purpose they are being used for.

@@

\paragraph{Defensive bidding} One negative consequence of using a closed economy,
in which the frameworks bid using currency which is entirely internal to the cluster,
%XXX mention this distinction elsewhere, and the fact that we can do either
is the possibility of \emph{hoarding}, in which one framework
declines to use any resources during a certain period so that it can amass
a much larger budget than any other resources.
It can then spend this budget at a future point in order to monopolize the cluster,
which may have undesirable consequences for frameworks that need uninterrupted service.

This can be prevented by using an appropriate bidding strategy
(in general we recommend modifying bidding strategies to achieve a desired
function whenever possible and leaving the scheduler itself as simple as possible).
A defensive bidder $A$ who receives an income equal to a $p$ fraction
of the cluster's resources can ensure the following invariant:
during any window of length $T$, $A$ spends roughly $p$ times the total amount
spent by all frameworks, and at every point in time $A$'s reserves are roughly equal to $p$
times the total reserves of all frameworks (where $T$ is an upper bound on how frequently auctions are conducted,
either the maximum length of a task or the period of time after which the resources used by a task
will be re-auctioned and potentially revoked).
In fact the second invariant follows from the first, which can be approximately attained
by simply scaling all bids during an interval of time $T$ to the appropriate level.

@@

By the definition of our auction, the price $p_B$ exceeds user A's willingness to pay for resources $R_B$ 
(or else user A's proxy would have continued bidding and the auction would not have concluded), 
while the price $p_A$ is less than user A's willingness to pay for resources $R_A$ 
(or else user A's proxy would have stopped bidding earlier). 
In particular, user A prefers their package to user B's package. 
Since at the start of the round user A preferred their allocation at their price to user B's allocation at user B's price, 
this property also holds at the end of the round. 
In this step we rely on our assumption that user A's valuations for their own holdings do not change after the auction is announced 
(otherwise it may be possible for user A to become envious in between rounds as more information is revealed, rather than during a round of the auction). 
We note in passing that similar assumptions are required to prove that DRF is envy-free in the dynamic setting,
even in a simple rather than realistic environment.
\qed
\end{pproof}

@@

When pricing information is provided, we show that the market-based mechanism can provide better performance than in DRF. As discussed in Section~\ref{examples}, there are many situations in which prices can be used to better encapsulate a framework's preferences. As a case study, we investigate one particular scenario of inhomogeneous performing resources.

@@

\subsection{Grid computing}
Job schedulers like TORQUE \cite{torque}, Condor \cite{condor}, and LSF
\cite{lsf} have long been used for solving the problem of resource allocation
within a high-performance-computing (HPC) or grid-computing environment.
For the most part, they do not use a two-level scheduling model like we do but
instead operate as a queue for predefined jobs which are run as resources become
available. Machines and job requirements also tend to show more homogeneity
within such environments (for example, the ratio between CPU, memory, and disk),
so the amount of optimization possible with pricing is lower.

@@

More generally, fair division is the problem in economics of dividing a set of
resources equitably among a set of people. Our problem differs somewhat from
fair division in that we don't seek to allocate every bit of the cluster to the
set of users. We assume that a user might be happy to have received nothing if
their value of gaining resources was too low compared to the others, since the
user keeps some amount of money unspent as a a result.

One of the economic fair division solutions is CEEI~\cite{moulin2004fair}, or
competitive equilibrium from equal incomes. This mechanism emulates a market
where participants initially receive an equal amount of resources and trade some
of them until each has the desired amount of resources. CEEI's use of a market
differs significantly from ours in that we do not use it only as a vehicle for
achieving a fair allocation, but also for frameworks to express their
preferences in a fine-grained way using prices and willingness to pay.

@@

In our evaluation, we showed through simulation the benefits of our protocol in the specific case of inhomogeneous performing resources. However, there are a number of other user constraints that should theoretically be better expressed using prices than existing methods. Future work would be to experimentally evaluate such cases. A few such user constraints include deadlines and varying latency sensitivities, differential service guarantees, deadweight losses of evictions, costs of fragmenting jobs, various execution types (e.g. speculative vs essential execution), and co-location of data or other important resources.

@@

\section{Acknowledgment}
